---
title: "Reproducible Document"
author: "rostools"
format: html
---

Setup makes the chunk run as the first 



```{r setup}
#| message: false
#| warning: false

library(tidyverse)

post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))

small_post_meal_data <- select(post_meal_data, id, BMI, Age, Group, auc_pg, auc_ins, glykemi)
```


```{r}
download.file(
  url = "https://zenodo.org/records/4989220/files/Eliasson_data2.csv?download=1",
  destfile = here::here("data/post-meal-insulin.csv")
)
```

## About me

- Marie Aarup Storgaard
- Department of hepatology and gastroenterologi, Aarhus University Hospital

*I* am a **PhD student**

## Simpel code

```{r}
3 * 3
```



## Writing R code

2+2


```{r}
head(airquality)
```

```{r}
weight_kilos <- 100
weight_kilos
```



```{r}
character <- c("a", "b", "c")
logic <- c(TRUE, TRUE, FALSE)
numeric <- c(1, 2, 3)
factor <- factor(c("low", "medium", "high"))
```



## Showing the data

```{r}
post_meal_data

glimpse(post_meal_data)
```


## Plot continous varibles

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram(na.rm = FALSE)
```


Af @fig-bmi-histo fremgår det, at ...

## Excercise: discrete plots

```{r}
#| fig-cap:  "Number of group participants"
#| label: fig-group

ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

see @fig-group above for a cool plot!

## Plotting two discrete variables

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Two figures side by side

```{r fig-bmi-glycemia}
#| fig-cap: "BMI and glykemi, side by side"
#| fig-subcap:
#|   - "Distribution of BMI"
#|   - "Number of those with glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```



## Plotting two continous variables

```{r}
#| fig-cap: "Scatterplot of BMI and the area under the curve for glucose"
#| label: gig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```
```{r}
head(post_meal_data)
```

## Selecting data

```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Age)

select(post_meal_data, id)
```

```{r}
select(post_meal_data, starts_with("PG"))

select(post_meal_data, ends_with("DXA"))

select(post_meal_data, contains("0"))
```

## Renaming columns 

```{r}
small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  )
```
